Understanding the technological transition based on cultural transmission biases during the Late Pleistocene in Korea

### 2020-05-15 analysis/paper/paper.Rmd
Move plots to note.rmd file

#Same as map but better view for summary
map_df(DF, cv)
box2 <- boxplot(cvmap) ##Is there any better way to show this data??

@@

cv_plot_site %>%
  pivot_longer(cols = -sitename, 
               names_to = "group") %>%
  ggplot(aes(x = sitename, 
             y = value, 
             fill = as.factor(group))) +
  geom_bar(stat = "identity", 
           position = position_dodge())

@@

direction_all+ direction_2 + direction_3 + plot_layout(ncol=1)
```

@@

xx_pca1_2 <- 
  data.frame(xx_pca2$x,
             stage = as.factor( df_sitename$SPstage.Stage[df_sitename$SPstage.Stage ==2]))

ggplot(xx_pca1_2 ,
       aes(PC1,
           PC2,
       colour = stage)) +
  geom_point() +
  stat_ellipse()

@@

xx_pca1_3 <- 
  data.frame(xx_pca3$x,
             stage = as.factor( df_sitename$SPstage.Stage[df_sitename$SPstage.Stage ==3]))

ggplot(xx_pca1_3 ,
       aes(PC1,
           PC2,
       colour = stage)) +
  geom_point() +
  stat_ellipse()

Contribution of variables for each of four PCA dimensions of ALL phases except for the first.

```{r}
library(gridExtra)
library(factoextra)
PC1_v <- fviz_contrib(xx_pca, choice = "var", axes = 1, top = 7)
PC2_v <- fviz_contrib(xx_pca, choice = "var", axes = 2, top = 7)
PC3_v <- fviz_contrib(xx_pca, choice = "var", axes = 3, top = 7)
PC4_v <- fviz_contrib(xx_pca, choice = "var", axes = 4, top = 7)

grid.arrange(PC1_v, PC2_v, PC3_v, PC4_v, nrow =2)

@@

correlate(SYG6_DF) %>% 
  network_plot()

@@

grid.arrange(SYG6_PC1_v, SYG6_PC2_v, nrow =1)

@@

correlate(SYG1_2DF) %>% 
  network_plot()

@@

grid.arrange(SYG1_2PC1_v, SYG1_2PC2_v, nrow =1)

@@

correlate(SYG1_1DF) %>% 
  network_plot()

@@

grid.arrange(SYG1_1PC1_v, SYG1_1PC2_v, nrow =1)

>>>>

#Same as map but better view for summary
map_df(DF, cv)

@@

@@

@@

@@

@@

@@

#grid.arrange(SYG6_PC1_v, SYG6_PC2_v, nrow =1)

@@

@@

#grid.arrange(SYG1_2PC1_v, SYG1_2PC2_v, nrow =1)

@@

@@

#grid.arrange(SYG1_1PC1_v, SYG1_1PC2_v, nrow =1)
